---
title: "Exponential Distribution"
author: "Lachlan Maxwell"
date: "August 18, 2014"
output: pdf_document
---

Simulation and exploration of the Central Limit Theorem in regards to Exponential Distribution

First we will simulate 1000 40 element exponential distributions, and calculate their means
```{r, echo=TRUE}

nosim <- 1000

lambda <- .2
n <- 40
cfunc <- function(x, n) sqrt(n) * (x - (1/lambda)) / (1/lambda)
AllMeans= NULL
NormalizedMean= NULL
AllSD = NULL
for (i in seq(1,nosim,1)) {
    x <- rexp(n, lambda)
    sample_mean <- mean(x)
    normalized_mean <- cfunc(sample_mean,n)
    standard_deviation <- sd(x)
    AllMeans=rbind(AllMeans,sample_mean)
    NormalizedMean=rbind(NormalizedMean, normalized_mean)
    
}
rownames(NormalizedMean) <- NULL
data = data.frame(NormalizedMean)

```
```{r, echo=FALSE}
theory_sample_mean_sd <- 1/sqrt(n) * (1/lambda)
real_sample_mean_sd <- sd(AllMeans)
sample_mean_mean <- mean(AllMeans)
```
The theoretical sample mean is:
```{r, echo=FALSE}
1/lambda
```
The actual population sample mean is:
```{r,echo=FALSE}
sample_mean_mean
```
The theoretical standard deviation of the sample mean is:
```{r,echo=FALSE}
theory_sample_mean_sd
```
The actual standard deviation of the sample mean is:
```{r,echo=FALSE}
library(ggplot2)
real_sample_mean_sd
```
All of the actual values are reasonably close to the theoretical values, suggesting a sufficiently large number of simulations with a large enough number of samples per simulation
The normalized mean has a distribution with approximately the same density as a normal distribution:
```{r}
g <- ggplot(data, aes(x = NormalizedMean)) + geom_histogram(alpha = .20, binwidth=.3, colour = "black", aes(y = ..density..)) 
g <- g + stat_function(fun = dnorm, size = 2)
print(g)
```


The percentage of sample means covered by the confidence interval for 1/lambda: X¯±1.96 * (S/sqrt(n) is
```{r}
ul <- mean(AllMeans) +  1.96 * real_sample_mean_sd
ll <- mean(AllMeans) -  1.96 * real_sample_mean_sd
inside <- 0
for (i in AllMeans) {
    if (i > ll & i < ul){
        inside <- inside + 1
    }
}
coverage <- inside/length(AllMeans)
coverage
```
This is the expected result, given the number of samples